Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-09-19 documents/TriangleScenarioArXiv/ts.tex
isolating final document for arxiv

% === All of the Packages I use frequently ===
\usepackage{../../packages/document_config}
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}

\renewcommand{\Events}[1]{\mathcal{S}\br{#1}} % This notation is conflicting

% === Causal structure formatting for tikz ===
\input{../../figures/causal_structures/formatting}

@@

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{nscenter}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{nscenter}
    \end{figure}

@@

            \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plotted_bits.pdf}

@@

    \begin{gather}
    \label[ineq]{eq:web_inequality}
        I\tsb{Web} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
    \end{gather}

@@

    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{nscenter}
    % \end{figure}
    As mentioned in \cref{sec:fritz_distribution}, this original proof of the non-classicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$. It is impossible to use Fritz's original argument to confirm non-classicality from an experimental point of view, because every laboratory-achievable distribution is subject to some amount of \text{noise}. One can minimize noise. e.g. by developing high-accuracy measurement channels, but \emph{perfect} correlations are unattainable. Causal compatibility inequalities such as  $I\tsb{Web}$ permit there to be noise within a set of observations before the ability to certify non-classicality breaks down.

@@

    % \begin{figure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    % \end{subfigure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    % \end{subfigure}
    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    % \end{figure}

@@

    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
            \vspace{-0.2in}
            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
            \label{fig:noisy_fritz}
    \end{nscenter}
    \end{figure}

@@

    \begin{gather}
        \label[ineq]{eq:symmetric_web_inequality}
        I\tsb{SymmetricWeb} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
    \end{gather}

@@

    % \subsection{Parameterizing Quantum Distributions}
    % \begin{figure}
    % \begin{nscenter}
    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
    %         \label{fig:triangle_structure_quantum_model}
    % \end{nscenter}
    % \end{figure}
    % An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization. Above, it was shown that our parameter space of choice was $2\pi$-periodic in all entries. Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to saturating $I\tsb{Web}$ instead of violating it. We observed that only parameters close enough to the \textit{Fritz parameters} (i.e. parameters that induce the Fritz distribution) were able to achieve violation of $I\tsb{Web}$.

@@

    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$. Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
        \label{fig:maximum_violation_I_1}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$. Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$. }
        \label{fig:maximum_violation_I_3}
    \end{nscenter}
    \end{figure}
    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
    %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$. While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
    %         \label{fig:symmetrized_fritz}
    % \end{nscenter}
    % \end{figure}

@@

    % \begin{figure}
    % \begin{subfigure}[t]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
    % \end{subfigure}
    % \begin{subfigure}[t]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
    % \end{subfigure}
    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
    % \end{figure}

@@

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{nscenter}

@@

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{nscenter}
    % \begin{definition}
    %     Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
    %     \begin{align*}
    %         \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
    %         \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
    %     \end{align*}
    % \end{definition}

@@

    % Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$. Another, albeit degenerate, parameterization of $\bc{p_i}$ involves beginning with $d$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_d}$, then forcing normalization by dividing each parameter $\la_i$ by the their sum.\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward eigenvalues that have similar values to each other.}.
    % \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
    % For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
    % % \subsection{Permutation Matrix}
    % % \label{sec:perm_matrix}
    % % \begin{figure}
    % %     \centering
    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
    % %     \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
    % %     \label{fig:perm_mtrx}
    % % \end{figure}
    % % Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure. For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}. Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}$. To illuminate its necessity, consider \cref{eq:triangle_Qcompatibility} in the absence of $\netperm$.
    % % \begin{align*}
    % % \prob[{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}} \br{M^a_{{A}}\otimes M^b_{{B}} \otimes M^c_{{C}}}}\\
    % % &= \Tr\bs{\br{\rho_{{AB}}M^a_{{A}}}\otimes\br{\rho_{{BC}}M^b_{{B}}}\otimes\br{\rho_{{CA}}M^c_{{C}}}}\\
    % % &= \Tr\br{\rho_{{AB}}M^a_{{A}}}\Tr\br{\rho_{{BC}}M^b_{{B}}}\Tr\br{\rho_{{CA}}M^c_{{C}}}\\
    % % &= \prob[{A}\mid \rho_{{AB}}]\br{a}\prob[{B}\mid \rho_{{BC}}]\br{b}\prob[{C}\mid \rho_{{CA}}]\br{c}
    % % \end{align*}
    % % On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$. This is analogously troubling for $B$ and $C$ as well. To resolve this issue, the permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$. To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
    % % \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
    % % $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''. It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
    % % \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    % \subsection{Computationally Efficient Parameterization of the Unitary Group}
    % \label{sec:comp_spengler}

>>>>

% === All of the Packages I use frequently ===
\usepackage{packages/document_config}

% === Causal structure formatting for tikz ===
\input{figures/causal_structures/formatting}

@@

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/triangle_structure}}
            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{nscenter}
        \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{nscenter}
    \end{figure}

@@

            \includegraphics[scale=0.6]{figures/distributions/fritz_dist_plotted_bits.pdf}

@@

    \begin{gather}
    \label[ineq]{eq:web_inequality}
        I\tsb{Web} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
    \end{gather}

@@

    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{nscenter}
    % \end{figure}
    As mentioned in \cref{sec:fritz_distribution}, this original proof of the non-classicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$. It is impossible to use Fritz's original argument to confirm non-classicality from an experimental point of view, because every laboratory-achievable distribution is subject to some amount of \text{noise}. One can minimize noise. e.g. by developing high-accuracy measurement channels, but \emph{perfect} correlations are unattainable. Causal compatibility inequalities such as  $I\tsb{Web}$ permit there to be noise within a set of observations before the ability to certify non-classicality breaks down.

@@

    % \begin{figure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017.pdf}}
    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    % \end{subfigure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017_lims.pdf}}
    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    % \end{subfigure}
    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    % \end{figure}

@@

    \begin{figure}
    \begin{nscenter}
            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/noise/noisy_yet_non_local_fritz.pdf}
            \vspace{-0.2in}
            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
            \label{fig:noisy_fritz}
    \end{nscenter}
    \end{figure}

@@

    \begin{gather}
        \label[ineq]{eq:symmetric_web_inequality}
        I\tsb{SymmetricWeb} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
    \end{gather}

@@

    % \subsection{Parameterizing Quantum Distributions}
    % \begin{figure}
    % \begin{nscenter}
    %         \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational}}
    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
    %         \label{fig:triangle_structure_quantum_model}
    % \end{nscenter}
    % \end{figure}
    % An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization. Above, it was shown that our parameter space of choice was $2\pi$-periodic in all entries. Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to saturating $I\tsb{Web}$ instead of violating it. We observed that only parameters close enough to the \textit{Fritz parameters} (i.e. parameters that induce the Fritz distribution) were able to achieve violation of $I\tsb{Web}$.

@@

    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$. Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
        \label{fig:maximum_violation_I_1}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$. Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$. }
        \label{fig:maximum_violation_I_3}
    \end{nscenter}
    \end{figure}
    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/symmetrized_fritz.pdf}
    %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$. While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
    %         \label{fig:symmetrized_fritz}
    % \end{nscenter}
    % \end{figure}

@@

    % \begin{figure}
    % \begin{subfigure}[t]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
    % \end{subfigure}
    % \begin{subfigure}[t]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
    % \end{subfigure}
    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
    % \end{figure}

@@

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{nscenter}

@@

    \begin{nscenter}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{nscenter}
    % \begin{definition}
    %     Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
    %     \begin{align*}
    %         \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
    %         \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
    %     \end{align*}
    % \end{definition}

@@

    % Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$. Another, albeit degenerate, parameterization of $\bc{p_i}$ involves beginning with $d$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_d}$, then forcing normalization by dividing each parameter $\la_i$ by the their sum.\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward eigenvalues that have similar values to each other.}.
    % \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
    % For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
    % % \subsection{Permutation Matrix}
    % % \label{sec:perm_matrix}
    % % \begin{figure}
    % %     \centering
    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{figures/perm_mtrx.pdf}
    % %     \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
    % %     \label{fig:perm_mtrx}
    % % \end{figure}
    % % Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure. For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}. Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}$. To illuminate its necessity, consider \cref{eq:triangle_Qcompatibility} in the absence of $\netperm$.
    % % \begin{align*}
    % % \prob[{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}} \br{M^a_{{A}}\otimes M^b_{{B}} \otimes M^c_{{C}}}}\\
    % % &= \Tr\bs{\br{\rho_{{AB}}M^a_{{A}}}\otimes\br{\rho_{{BC}}M^b_{{B}}}\otimes\br{\rho_{{CA}}M^c_{{C}}}}\\
    % % &= \Tr\br{\rho_{{AB}}M^a_{{A}}}\Tr\br{\rho_{{BC}}M^b_{{B}}}\Tr\br{\rho_{{CA}}M^c_{{C}}}\\
    % % &= \prob[{A}\mid \rho_{{AB}}]\br{a}\prob[{B}\mid \rho_{{BC}}]\br{b}\prob[{C}\mid \rho_{{CA}}]\br{c}
    % % \end{align*}
    % % On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$. This is analogously troubling for $B$ and $C$ as well. To resolve this issue, the permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$. To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
    % % \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
    % % $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''. It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
    % % \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    % \subsection{Computationally Efficient Parameterization of the Unitary Group}
    % \label{sec:comp_spengler}
